```{r data generation, echo = FALSE, results = "hide"}
## DATA GENERATION
mu = sample(50+(0:20)*10, 1)
sig = sample(2:round(mu/3,0), 1)
n = sample(60:200,1)
se = round(sig/sqrt(n),2) 

z = round(runif(1,-2.7,2.7),2)
la = round(pnorm(z),3)
x = round(mu+z*se,2)

Pr = round(pnorm(z),3)
```

Question
========

A roughly symmetric population has a mean $\mu = `r mu`$ and standard deviation $\sigma = `r sig`$. What is the probability that a sample of size $n = `r n`$ has a mean less than $`r x`$?


Solution
========

Find the standard error.
$$SE = \frac{\sigma}{\sqrt{n}} = \frac{`r sig`}{\sqrt{`r n`}} = `r se` $$
Describe the sampling distribution.
$$\bar{X} \sim \mathcal{N}(`r mu`,\,`r se`) $$

Draw a sketch.
\
```{r normal_sketch_sampling, echo = FALSE, results = "hide", fig.height = 3, fig.width = 7, fig.path = "", fig.cap = ""}
par(mar=c(5,3,1,1))
zs = seq(-3,3,length=1000)
ys = dnorm(zs)
plot(zs, ys, 'l',xlim = c(-3,3), ylim = c(0,0.4),
     ann=FALSE,xaxt="n",yaxt="n",
     lwd=1,bty='n')
axis(side=1, line=0, at=-3:3, labels = FALSE)
mtext(mu+(-3:3)*se,side=1,line=0.5,at=-3:3)
mtext(c("xbar="),line=0.5,side=1,at=-3.5)
axis(side=1, line=2,at=-3:3, labels = FALSE)
mtext(-3:3,side=1,line=2.5,at=-3:3)
mtext(c("z="),line=2.5,side=1,at=-3.5)
polygon(c(zs[zs<=z], z, -3),c(ys[zs<=z], 0, 0), col=rgb(1,0,0,0.5))
lines(c(-3,3),c(0,0),'l')
text(-2,0.3,label=sprintf("area = P(Xbar < %0.2f)",x))
```

Calculate a $z$ score.
$$z = \frac{`r x`-`r mu`}{`r se`} = `r z` $$
Determine the probability.
$$P(X<`r x`) = `r Pr` $$


Meta-information
============
extype: string
exsolution: $P(X<`r x`) = `r Pr` $
exname: sampling distro
extol: 0.01
