```{r data generation, echo = FALSE, results = "hide"}
options(scipen=999)
## DATA GENERATION
while(T)
{
    p1 = round(runif(1,0.01,0.99),3)
    p2 = round(runif(1,0.01,0.99),3)
    dp = p2-p1
    n1 = sample(1:10,1)*10^sample(1:3,1)
    n2 = sample(1:10,1)*10^sample(1:3,1)
    se = signif(sqrt(p1*(1-p1)/n1+p2*(1-p2)/n2),3)
    is_norm1 = (p1*n1>10 & (1-p1)*n1>10)
    is_norm2 = (p2*n2>10 & (1-p2)*n2>20)
    if(is_norm1 & is_norm2 & se>0.005)
    {
        break
    }
}
z = round(runif(1,0.2,2.6),2)
dphat = round(z*se+dp,3)
z = round((dphat-dp)/se,2)
Pr = 2*round(pnorm(abs(z)),4) - 1
ddp = dphat-dp
adj = sample(c("cold","angry","sorry","abysmal",
               "happy", "preoccupied", "sick", "green",
               "fluorescent", "folksy", "reclusive", "omnivorous",
               "special"), 1)
```


Question
========

In one population, `r 100*p1`% are `r adj` ($p_1 = `r p1`$). In a second population, `r 100*p2`% are `r adj` ($p_2 = `r p2`$). When random samples of sizes `r n1` and `r n2` are taken from the first and second populations respectively, what is the chance that $\hat{p}_2 - \hat{p}_1$ is between `r signif(dp-abs(ddp),3)` and `r signif(dp+abs(ddp),3)`?


Solution
========

Check if we expect the $\hat{P}_2 - \hat{P}_1$ sampling to follow a normal distribution. The random sampling from two (presumably very large) populations allows us to assume independence. The inequalities are also satisfied:
\begin{align*}
n_1 p_1 &> 10 \\
n_1 (1-p_1) &> 10\\
n_2 p_2 &> 10 \\
n_2 (1 -p_2) &> 10
\end{align*}
Calculate the expected difference.
\begin{align*}
p_2-p_1 &= `r p2`-`r p1`\\
   &= `r dp`
\end{align*}
Calculate the standard error.
\begin{align*}
SE &= \sqrt{\frac{p_1(1-p_1)}{n_1}+\frac{p_2(1-p_2)}{n_2}}\\\\
   &= \sqrt{\frac{`r p1`(1-`r p1`)}{`r n1`}+\frac{`r p2`(1-`r p2`)}{`r n2`}}\\\\
   &= `r se`
\end{align*}
Determine $z$ scores.
\begin{align*}
z_\text{lower}  &= \frac{(\hat{p}_2-\hat{p}_1)_\text{lower}-(p_2-p_1)}{SE} \\\\
   &= \frac{(`r dp-abs(ddp)`) - (`r dp`)}{`r se`} \\\\
   &= `r -abs(z)`\\\\
z_\text{upper}  &= \frac{(\hat{p}_2-\hat{p}_1)_\text{upper}-(p_2-p_1)}{SE} \\\\
   &= \frac{(`r dp+abs(ddp)`) - (`r dp`)}{`r se`} \\\\
   &= `r abs(z)`
\end{align*}
Draw a sketch. The phrase "between `r signif(dp-abs(ddp),3)` and `r signif(dp+abs(ddp),3)`" suggests finding a central area.

```{r diff_sampling_central_area, echo = FALSE, results = "hide", fig.height = 3, fig.width = 6, fig.path = "", fig.cap = ""}
par(mar=c(5,3,1,1))
zs = seq(-3,3,length=1000)
ys = dnorm(zs)
plot(zs, ys, 'l',xlim = c(-3,3), ylim = c(0,0.4),
     ann=FALSE,xaxt="n",yaxt="n",
     lwd=1,bty='n')
axis(side=1, line=0, at=-3:3, labels = FALSE)
mtext(round(p2-p1+(-3:3)*se,3),side=1,line=0.5,at=-3:3)
mtext(c("p2-p1="),line=0.5,side=1,at=-3.6)
axis(side=1, line=2,at=-3:3, labels = FALSE)
mtext(-3:3,side=1,line=2.5,at=-3:3)
mtext(c("z="),line=2.5,side=1,at=-3.7)
polygon(c(zs[zs>=-abs(z) & zs<=abs(z)], abs(z), -abs(z)),c(ys[zs>=-abs(z) & zs<=abs(z)], 0, 0), col=rgb(1,0,0,0.5))
lines(c(-3,3),c(0,0),'l',lwd=1)
```

Use a z table.
\begin{align*}
\text{Pr}\left(`r signif(dp-ddp,3)` < \hat{P}_2 - \hat{P}_1 < `r signif(dp+ddp,3)`\right) &= \text{Pr}(|Z|<`r z`) \\
&= 2\cdot\Phi(`r abs(z)`)-1 \\
&= `r Pr`
\end{align*}

Thus, we conclude that there is a `r Pr*100`% chance that $\hat{P}_2-\hat{P}_1$ is between `r signif(dp-abs(ddp),3)` and `r signif(dp+abs(ddp),3)`.


Meta-information
============
extype: num
exsolution: `r Pr`
exname: p diff sampling central area
extol: 0.01
