```{r data generation, echo = FALSE, results = "hide"}
## DATA GENERATION
shape1 = 2**runif(1,-1,1)
shape2 = 2**runif(1,-1,1)
n1 = sample(5:10,1)
n2 = sample(5:10,1)
mag = sample(-1:3,1)
scale = 10^mag
offset = runif(1,0,10)*scale
data = sort(round(rbeta(n1*n2,shape1,shape2)*scale + offset,-mag+2))

pick = sample(2:(n1*n2-1),1)
num = data[pick]

pick = 0
for(i in 1:(n1*n2))
{
    if (data[i] <= num)
    {
        pick = i
    }
}

perc = pick/n1/n2
```

Question
========

From the sorted data shown below ($n = `r n1*n2`$), determine the percentile of `r num`.

```{r display generation,echo = FALSE, results = "hide"}
disp = '|'
for(i in 1:n2)
{
    disp = paste(c(disp,'\t column',i,'\t|'),collapse='')
}
disp = paste(c(disp,'\n|'),collapse='')
for(i in 1:n2)
{
    disp = paste(c(disp,'---------|'),collapse='')
}
#disp = paste(c(disp,'\n'),collapse='')
for(i in 1:n1)
{
    disp = paste(c(disp,'\n|'),collapse='')
    for(j in 1:n2)
    {
        disp = paste(c(disp,data[(j-1)*n1+i],'|'),collapse='')
    }
}
```

`r disp`


Solution
========

Remember, the percentile of a value is equal to the percent of data that are less than or equal to that value. We find the index of `r num`. If there are multiple instances, we take the highest index.

$$i = `r pick`$$

To determine the percentile, we divide this index by the sample size.

$$\begin{aligned}
    \ell &= \frac{i}{n} \\
         &= \frac{`r pick`}{`r n1*n2`} \\
         &= `r signif(perc,4)`
\end{aligned}$$

Meta-information
============
extype: string
exsolution: `r signif(perc,4)` 
exname: find percentile
extol: 0.01
