```{r data generation, echo = FALSE, results = "hide"}
## DATA GENERATION
shape1 = 2**runif(1,-1,1)
shape2 = 2**runif(1,-1,1)
n1 = sample(5:10,1)
n2 = sample(5:8,1)
mag = sample(-1:3,1)
scale = 10^mag
offset = runif(1,0,10)*scale
data = sort(round(rbeta(n1*n2,shape1,shape2)*scale + offset,-mag+2))
h = hist(data,density=20)

## The frequency table
ft = ''
ft = paste(c(ft, paste(c('| $', h$breaks[1], '\\le X \\le ', h$breaks[2], '$| ', h$counts[1], ' |'),collapse=''), '\n'),collapse='')
for(i in 2:length(h$counts))
{
    ft = paste(c(ft, paste(c('| $', h$breaks[i], '< X \\le ', h$breaks[i+1], '$| ', h$counts[i], ' |'),collapse=''), '\n'),collapse='')
}
```

Question
========

Please make a histogram from the following (sorted) data ($n = `r n1*n2`$).

```{r display generation,echo = FALSE, results = "hide"}
disp = '|'
for(i in 1:n2)
{
    disp = paste(c(disp,'\t column',i,'\t|'),collapse='')
}
disp = paste(c(disp,'\n|'),collapse='')
for(i in 1:n2)
{
    disp = paste(c(disp,'---------|'),collapse='')
}
#disp = paste(c(disp,'\n'),collapse='')
for(i in 1:n1)
{
    disp = paste(c(disp,'\n|'),collapse='')
    for(j in 1:n2)
    {
        disp = paste(c(disp,data[(j-1)*n1+i],'|'),collapse='')
    }
}
```

`r disp`

Please use a lowest boundary of `r h$breaks[1]` and a bin width of `r h$breaks[2]-h$breaks[1]`. Also, if a value falls directly on a break, place it in the lower bin.



Solution
========

We can make a frequency table.

| Condition | Count |
|:---------:|:-----:|
`r ft`

\
```{r hist, echo = FALSE, results = "hide", fig.height = 4, fig.width = 5, fig.path = "", fig.cap = ""}
hist(data,density=20)
```
\


Meta-information
============
extype: string
exsolution: make the histogram
exname: histogram
extol: 0.01
