```{r data generation, echo = FALSE, results = "hide"}
## DATA GENERATION
shape1 = 2**runif(1,-1,1)
shape2 = 2**runif(1,-1,1)
n = sample(3:6,1)*5
mag = sample(-1:3,1)
scale = 10^mag
offset = runif(1,0,10)*scale
data = round(rbeta(n,shape1,shape2)*scale + offset,-mag+2)
h = hist(data,density=20)


## The frequency table
ft = ''
for(i in 1:length(h$counts))
{
    ft = paste(c(ft, paste(c('| $', h$breaks[i], '< X \\le ', h$breaks[i+1], '$| ', h$counts[i], ' |'),collapse=''), '\n'),collapse='')
}
```

Question
========

Please make a histogram from the following (sorted) data.

`r matrix(sort(data), nrow = 5)`

Please use a lowest boundary of `r h$breaks[1]` and a bin width of `r h$breaks[2]-h$breaks[1]`. Also, if a value falls directly on a break, place it in the lower bin.



Solution
========

We can make a frequency table.

| Condition | Count |
|:---------:|:-----:|
`r ft`

\
```{r hist, echo = FALSE, results = "hide", fig.height = 4, fig.width = 5, fig.path = "", fig.cap = ""}
hist(data,density=20)
```
\


Meta-information
============
extype: string
exsolution: make the histogram
exname: histogram
extol: 0.01
