```{r data generation, echo = FALSE, results = "hide"}
## DATA GENERATION
while(T){
    p = round(runif(1,0.09,0.91),3)
    n = sample((1:50) *100,1)
    se = signif(sqrt(p*(1-p)/n),2)
    z = round(runif(1,0.2,2.5),2)
    if (n*p>10 & n*(1-p)>10 & sqrt(n*p*(1-p))>15 & abs(z-100*(phat-p))>0.3)
    {
        break
    }
}
phat = round(p+z*se,3)
z = round((phat-p)/se,2)
Pr = round(2*pnorm(-z),4)
wrd = sample(c('sad','angry','special','greedy','bad','great','strong','happy','popular','cold'),1)
wrd2 = sample(c('outside', 'beyond', 'farther than','NOT between'),1)
delp = phat-p
pup = p+delp
plo = p-delp 
```

Question
========

In a very large population, `r p*100`% are `r wrd`. When a random sample of size `r n` is taken, what is the chance that the sample proportion of `r wrd` individuals is `r wrd2`  $\pm$ `r delp*100` percentage points from `r p*100`%? 


Solution
========

Determine the standard error.
$$SE = \sqrt{\frac{p(1-p)}{n}} = \sqrt{\frac{`r p`(1-`r p`)}{`r n`}} = `r se` $$
Determine the upper and lower bounds on $\hat{p}$.
$$\hat{p}_{\text{lower}} = `r p`-`r phat-p` = `r p-(phat-p)` $$
$$\hat{p}_{\text{upper}} = `r p`+`r phat-p` = `r p+(phat-p)` $$
Determine the $z$ scores. For simplicity, we ignore the continuity correction.
$$z_{\text{lower}} = \frac{\hat{p}_{\text{lower}}-p}{SE} = \frac{`r p-(phat-p)`-`r p`}{`r se`} = 
\frac{`r -(phat-p)`}{`r se`} = `r -z` $$
$$z_{\text{upper}} = \frac{\hat{p}_{\text{upper}}-p}{SE} = \frac{`r phat`-`r p`}{`r se`} = \frac{`r phat- p`}{`r se`} = `r z` $$
We are looking for a two-tail area ("`r wrd2`  $\pm$ `r (phat-p)*100` percentage points from `r p*100`%").

```{r phat_sampling_outer, echo = FALSE, results = "hide", fig.height = 3, fig.width = 6, fig.path = "", fig.cap = ""}
par(mar=c(5,3,1,1))
zs = seq(-3,3,length=10000)
ys = dnorm(zs)
plot(zs, ys, 'l',xlim = c(-3,3), ylim = c(0,0.4),
     ann=FALSE,xaxt="n",yaxt="n",
     lwd=1,bty='n')
axis(side=1, line=0, at=-3:3, labels = FALSE)
mtext(p+(-3:3)*se,side=1,line=0.5,at=-3:3)
mtext(c("phat="),line=0.5,side=1,at=-3.6)
axis(side=1, line=2,at=-3:3, labels = FALSE)
mtext(-3:3,side=1,line=2.5,at=-3:3)
mtext(c("z="),line=2.5,side=1,at=-3.6)
polygon(c(zs[zs<=-z], -z, -3),c(ys[zs<=-z], 0, 0), col=rgb(1,0,0,0.5))
polygon(c(zs[zs>=z], 3, z),c(ys[zs>=z], 0, 0), col=rgb(1,0,0,0.5))
lines(c(-3,3),c(0,0),'l',lwd=1)
```

To determine that central area, we use the z table.
$$\text{Pr}\left(|\hat{P}-`r p`| > `r phat-p`\right) ~~=~~ \text{Pr}\left(|Z| > `r z`\right) ~~=~~ 2\cdot\Phi(`r -z`) ~~=~~ `r Pr` $$
Thus, we conclude there is a `r signif(100*Pr,3)`% chance that the sample proportion is `r wrd2`  $\pm$ `r (phat-p)*100` percentage points from `r p*100`%. 

Meta-information
============
extype: num
exsolution: `r Pr`
exname: phat sampling outer prob
extol: 0.01
